My title

### 2024-04-19 paper/paper.qmd
added results section

We found that some metrics such as individual kill/death ratios have a significant positive correlation with win rates while other metrics such as the total number of rounds played has no correlation with win rate.

@@

The final dataset consists of 445 players with a cumulative 9855 maps played across 22 tournaments. For each player, the dataset contains the number of tournament maps won and lost. A map is won if their team wins 13 of the first 24 rounds or if they win 4 out of 6 rounds in overtime.
The dataset also contains the number of kills, deaths, HS % (headshot percentage), ADR, and the total number of rounds played. These statistics are measured over 
the player's professional career. HS % is measured as the proportion of kills where the killing blow is a headshot and ADR is measured as the total damage done to
enemies divided by the number of rounds played.

@@

HS % is a metric of the player's mechanical skill, which should be part of determining their ability to win fights.
Then similar to K/D, we should also expect HS % to be positively correlated with win rates.

Finally, the number of rounds played can be used to determine the experience of a player, with more experienced players having played more rounds.
We expect more experienced players to be better, so it should be positively correlated with win rates.

# Results
```{r}

```
```{r}
#| label: tbl-model
#| tbl-cap: Whether a respondent is likely to vote for Biden based on their race and education
#| echo: false
#| warning: false

modelsummary(
  list("Tournament Win Rate" = winrates),
  statistic = "mad",
  )
```

@@

# Appendix {-}

# References

>>>>

We found that some metrics such as K/D have a positive correlation with win rates while other metrics such ADR have negative correlations with win rate.

@@

The final dataset consists of 445 players with a cumulative 9855 maps played across 22 tournaments. For each player, the dataset contains the number of tournament maps won and lost. A map is won if their team wins 13 of the first 24 rounds or if they win 4 out of 6 rounds in overtime.
The dataset also contains the number of kills, deaths, HS% (headshot percentage), ADR, and the total number of rounds played. These statistics are measured over 
the player's professional career. HS% is measured as the proportion of kills where the killing blow is a headshot and ADR is measured as the total damage done to
enemies divided by the number of rounds played.

@@

HS% is a metric of the player's mechanical skill, which should be part of determining their ability to win fights.
Then similar to K/D, we should also expect HS% to be positively correlated with win rates.

The number of rounds played can be used to determine the experience of a player, with more experienced players having played more rounds.
Additionally, better players should play in the professional scene more, so they should have more rounds played in total.
Given these factors, we expect the number of rounds played to be positively correlated with win rates.

# Results
@fig-kdr-wr shows the relationship between K/D and map win rates with a line provided by the linear regression model.
The overall relationships in this figure and following figures are difficult to see using only data points due to the number and distribution.
However, the regression line suggests there is a positive correlation between K/D and win rate, as expected when constructing the model.

```{r}
#| label: fig-kdr-wr
#| fig-cap: Win rate by kill/death ratio with regression line
#| echo: false
plot_predictions(winrates, condition = "kill_death_ratio") +
  geom_point(data = data, aes(x = kill_death_ratio, y = win_percent), alpha = 0.5) +
  labs(x = "Kill/Death Ratio", y = "Win Rate") +
  theme_classic()
```

@fig-hs-wr shows the relationship between HS% and map win rates with a line provided by the linear regression model.
The regression line suggests there is a positive correlation between HS% and win rate, as expected when constructing the model.
```{r}
#| label: fig-hs-wr
#| fig-cap: Win rate by headshot percentage with regression line
#| echo: false
plot_predictions(winrates, condition = "hs") +
  geom_point(data = data, aes(x = hs, y = win_percent), alpha = 0.5) +
  labs(x = "Headshot Percentage", y = "Win Rate") +
  theme_classic()
```
@fig-adr-wr shows the relationship between ADR and map win rates with a line provided by the linear regression model.
Interestingly, the regression line suggests there is a negative correlation between ADR and win rate.
This appears to be counterintuitive since more damage is generally good. An explanation for this could be 
overaggressive players deal more damage but leave their teams in a worse position, leading to lower win rates. 
Another explanation could be "baiting", where a player waits for their team members to distract enemies in order to have easier kills,
allowing them to stay alive, inflating their personal stats but reducing the chance for their team to win.
```{r}
#| label: fig-adr-wr
#| fig-cap: Win rate by ADR with regression line
#| echo: false
plot_predictions(winrates, condition = "adr") +
  geom_point(data = data, aes(x = adr, y = win_percent), alpha = 0.5) +
  labs(x = "Average Damage per Round", y = "Win Rate") +
  theme_classic()
```
@fig-rounds-wr shows the relationship between total number of rounds played and map win rates with a line provided by the linear regression model.
The regression line suggests there is a positive relationship between total rounds played and win rate, as expected when constructing the model.
```{r}
#| label: fig-rounds-wr
#| fig-cap: Win rate by total rounds played with regression line
#| echo: false
plot_predictions(winrates, condition = "rounds") +
  geom_point(data = data, aes(x = rounds, y = win_percent), alpha = 0.5) +
  labs(x = "Rounds Played", y = "Win Rate") +
  theme_classic()
```
@tbl-model shows the model coefficients. Note this is not standardized, so the coefficient for K/D is large since a $\pm$ 0.1 change in K/D is a large difference whereas the coefficient for number of rounds is tiny since a change of $\pm$ 1 round played is practically nothing.

@fig-model-confidence shows the confidence intervals for the model predictors.
```{r}
#| label: tbl-model
#| tbl-cap: Player win rate based on K/D, HS%, ADR, and rounds played
#| echo: false
#| warning: false

modelsummary(
  list("Tournament Map Win Rate" = winrates),
  statistic = "mad",
  fmt = 6
  )
```

@@

# Appendix {-}
```{r}
#| label: fig-model-confidence
#| fig-cap: Confidence intervals for predictors win rate
#| echo: false

modelplot(winrates, conf_level = 0.95) +
  labs(x = "95 percent confidence interval")
```
# References
